### 2016-08-29 Chapters/PaperSummary.tex
Contributions written

% Very ugly
\epigraph{\textonehalf\,\,research\,\,\,\,\,\,\,\,\,\,\,\,and \textonehalf\,\,\,\,\,\,\,\,Tεχνη

          \textonehalf\,\,observation,\,\,\,\,\,\,\,\,\,\,\,\,\textonehalf\,\,\,\,\,\,\,\,Tεχνη

          \textonehalf\,\,training,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\textonehalf\,\,\,\,\,\,\,\,Tεχνη}{
  --- \textsc{Ezra Pound}, \textit{Canto LXXXV}}

@@

I contributed the theoretical derivation of the quantum/classical polarizable
terms in a four-component \acs{SCF} framework, for energies and linear response
properties. I devised the coupling of the four-component program \DIRAC with
\pcmsolver by providing the implementation and testing of:
\begin{itemize}
  \item \acs{MEP} integrals for four-component wave functions,
  \item the additional Fock matrix contributions,
  \item the additional terms in the response equations.
\end{itemize}
I performed all the calculations and large part of the data analysis
for the results reported in the paper.
Finally, I wrote the first draft of the paper and coordinated editing of
all subsequent versions.

@@

For this paper, I provided template interface and test sets for the cavity
generator\autocite{Harbrecht2009-no, Harbrecht2011-dk} and wavelet Galerkin
\acs{BEM} solver with \pcmsolver.
These were used to interface with the new C++ implementation of the wavelet
Galerkin solvers of Monica Bugeanu.
I implemented the interface between the \LSDALTON quantum chemistry software
package and the \pcmsolver software library. The interface allows to run \acs{HF} and
\acs{KS}-\acs{DFT} single-point and linear response calculations.
I, together with coauthor Krzysztof Mozgawa, performed the benchmark quantum
chemical calculations presented in the paper.
Finally, I coordinated the editing of all manuscript drafts. I wrote Sections 2.1 and 2.3,
while Sections 3 and 4 were co-written with the first author, Monica Bugeanu.
I performed most of the data analysis and produced tables and graphs.

@@

I contributed most of the theoretical work for this paper, based on early drafts from coauthors
Ville Weijo and Hui Cao. In particular, I derived the separation of
the Coulomb singularity in its final form.
Moreover, I contributed the implementation and testing of the Green's function code.
The interface to the \LSDALTON program package, developed within paper II, was
also used for this paper.
I wrote the first draft of the paper and coordinated all subsequent editing stages.

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Relativistic calculation of EPR and pNMR parameters in solution}
\section*{Paper IV: Relativistic calculation of EPR and pNMR parameters in solution}

@@

>>>>

\epigraph{\textonehalf\,\,research \kern 20pt and \textonehalf \kern 20pt \textgreek{Tέχνη}

          \textonehalf\,\,observation, \kern 22pt \textonehalf \kern 20pt \textgreek{Tέχνη}

          \textonehalf\,\,training, \kern 39pt \textonehalf \kern 20pt \textgreek{Tέχνη}
          }{
  --- \textsc{Ezra Pound}, \textit{Canto LXXXV}}

@@

I contributed the theoretical derivation of the quantum/classical polarizable
terms in a four-component \acs{SCF} framework, for energies and linear response
properties. I devised the coupling of the four-component program \DIRAC with
\pcmsolver by providing the implementation and testing of:
\begin{enumerate*}[label={\alph*)},font={\color{PMS1797}}]
  \item \acs{MEP} integrals for four-component wave functions,
  \item the additional Fock matrix contributions and
  \item the additional terms in the response equations.
\end{enumerate*}
I performed all the calculations and large part of the data analysis
for the results reported in the paper.
Finally, I wrote the first draft of the paper and coordinated editing of
all subsequent versions.

@@

For this paper, I provided template interface and test sets for the cavity
generator\autocite{Harbrecht2009-no, Harbrecht2011-dk} and wavelet Galerkin
\acs{BEM} solver with \pcmsolver.
These were used to interface with the new C++ implementation of the wavelet
Galerkin solvers of Monica Bugeanu.
I implemented the interface between the \LSDALTON quantum chemistry software
package and the \pcmsolver software library. The interface allows to run \acs{HF} and
\acs{KS}-\acs{DFT} single-point and linear response calculations.
Together with coauthor Krzysztof Mozgawa, I performed the benchmark quantum
chemical calculations presented in the paper.
Finally, I coordinated the editing of all manuscript drafts.
In particular, I wrote the first draft of Sections 2.1 and 2.3.
The first draft of Sections 3 and 4 was co-written with the first author, Monica Bugeanu.
I performed most of the data analysis and produced tables and graphs.

@@

I contributed the theoretical work for this paper, based on earlier drafts from coauthors
Ville Weijo and Hui Cao. In particular, I derived the separation of
the Coulomb singularity in its final form.
Moreover, I contributed the implementation and testing of the Green's function code.
The interface to the \LSDALTON program package, developed within paper II, was
also used for this paper.
I wrote the first draft of the paper and coordinated all subsequent editing stages.

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Relativistic Calculation of EPR and pNMR Parameters in Solution}
\section*{Paper IV: Relativistic calculation of EPR and pNMR parameters in solution}

My contributions to this paper include prototyping the interface between the
\pcmsolver library and the \ReSpect quantum chemistry code.
The interface is maintained in collaboration with coauthor Michal Repisky, who also
refined the implementation to achieve better computational performance.
I tested the interface against one-component and four-component results obtained with
the \LSDALTON and \DIRAC codes, respectively.
I helped coauthors Michal Repisky, Stanislav Komorovsky and Peter Hrobarik
with setting up the \acs{PCM} calculations described in the paper.
Finally, I provided the first draft for Section 2 of the paper and took part in all editing stages.
The interface to \ReSpect will be released in the next public version of the software
package, providing \acs{PCM} and \acs{COSMO} capabilities.

@@

I developed the theoretical framework for the open-ended \acs{SCF} formulation
of molecular response properties when a quantum/classical polarizable continuum
Hamiltonian is used.~\autocite{Thorvaldsen2008-sg, Lipparini2010-be}
I provided its implementation within the \DALTON code, by interfacing the
\pcmsolver library and the open-ended \acs{SCF} response code of
\citeauthor{Ringholm2014-gx}~\autocite{Ringholm2014-gx, Friese2015-kb}
I performed extensive testing of the code by comparing with previously
published implementations of the \acs{PCM}-\acs{SCF} response functions within
\DALTON.~\autocite{Cammi2003-qy, Frediani2005-nc, Ferrighi2010-pm}
Together with coauthors Maarten T.~P.~Beerepoot and Yann Cornaton, I carried out
the multiphoton absorption calculations presented in the paper. I contributed
to data collection and data analysis.
I drafted the initial versions of Sections 2 and 3 of the manuscript and coordinated all
editing stages with coauthor Maarten T. P. Beerepoot.
